Calculate FD

### 2020-09-11 analysis/calc_fd.Rmd
Calculate FD based on the weight column, read in plots as characters

  species_mat <- data %>%
    group_by(year, id) %>%
    summarise(abun = sum(sum_abundance)) %>%
    ungroup() %>%
    arrange(year) %>%
    arrange(id) %>%
    pivot_wider(names_from = id, values_from = abun, values_fill = 0) %>%
    select(-year)

@@

  trait_mat <- data %>%
    select(-c(taxa, record_id, day, month, year, sample_desc, id_species, 
              latitude, longitude, sum_abundance, sum_biomass, traitName, 
              biotimeName, scientificName)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(na.omit(.))) > 1) #remove columns that have the same value for all columns

@@

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = TRUE, m = "min", ...))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])
    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>% 
  ungroup() #%>%
  #filter(#!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327, 195)) #exclude to get the file size smaller
```

@@

fd_data <- files %>%
  paste0(here::here("data", "fd_output"), "/", .) %>%
  map_dfr(read_tsv)

@@

#get_fd_error <- safely(get_fd)
#system.time(fd <- map(plot_sizes$plot_id, get_fd_error, obs_data = data, corr = "cailliez"))
system.time(fd <- map(plot_sizes$plot_id, get_fd_safe, obs_data = data, corr = "cailliez"))
```

@@

Format tables
```{r}
fd_table <- fd_data %>% 
  select(year, plot_id, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  left_join(biotime_traits %>% 
              select(plot_id, study_id, plot) %>% 
              mutate(plot_id = as.numeric(plot_id)) %>%
                       distinct())

>>>>

  # #check which column the abundaces weights are stored in (abundance or biomass)
  # if (sum(data$year_abun) == 0) {weight <- "year_biomass"} else {weight <- "year_abun"}

  species_mat <- data %>%
    select(year, id, weight) %>%
    arrange(year) %>%
    arrange(id) %>%
    pivot_wider(names_from = id, values_from = weight, values_fill = 0) %>%
    select(-year)

@@

  trait_mat <- data %>%
    select(-c(biotimeName, taxa, id_species, plot, year, weight, 
              traitName, scientificName, plot_id, study_id)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(na.omit(.))) > 1)  #remove columns that have the same value for all columns

@@

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = TRUE, ...))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])
    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>% 
  filter(plot_id != "169A") %>% #soemthing strange going on with this one, a duplicate species obs in 2006
  ungroup() #%>%
  #filter(#!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327, 195)) #exclude to get the file size smaller

plots <- data %>%
  pull(plot_id) %>%
  unique()

system.time(fd <- map(plots, get_fd_safe, obs_data = data, m = "min", corr = "cailliez"))
```

@@

fd_data <- files %>%
  paste0(here::here("data", "fd_output"), "/", .) %>%
  map_dfr(~read_tsv(.x, col_types = "dddddddddcd")) #%>% mutate(plot_id = as.character(plot_id)))

@@

get_fd_error <- safely(get_fd)
system.time(fd <- map(plot_sizes$plot_id, get_fd_error, obs_data = data, m = "min", corr = "cailliez"))
system.time(fd <- map(plot_sizes$plot_id, get_fd_safe, obs_data = data,  m = "min", corr = "cailliez"))
```

@@

Format tables
```{r}
fd_table <- fd_data %>% 
  select(year, plot_id, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  left_join(biotime_traits %>% 
              select(plot_id, study_id, plot) %>%
                       distinct())
